---
title: "Step 4A SQL Exploration"
subtitle: "Steam 3,000-game market sample"
format:
  html:
    toc: true
    number-sections: true
execute:
  echo: false
---

```{r}
source("../R/db_connect.R")
project_root <- find_project_root()
result_path <- function(name) {
  file.path(project_root, "data", "analysis", "sql", paste0(name, ".csv"))
}
read_result <- function(name) read.csv(result_path(name), check.names = FALSE)

db_counts <- with_steam_db(function(con) {
  DBI::dbGetQuery(
    con,
    paste(
      "SELECT",
      "(SELECT COUNT(*) FROM games) AS games,",
      "(SELECT COUNT(*) FROM review_snapshots) AS review_snapshots,",
      "(SELECT COUNT(*) FROM game_genres) AS game_genres,",
      "(SELECT COUNT(*) FROM genres) AS genres,",
      "(SELECT COUNT(*) FROM vw_model_sample_20) AS model_sample"
    )
  )
})
stopifnot(
  db_counts$games[[1]] == 3000,
  db_counts$review_snapshots[[1]] == 3000,
  db_counts$game_genres[[1]] == 8796,
  db_counts$genres[[1]] == 13,
  db_counts$model_sample[[1]] == 844
)

market <- read_result("market_overview")
price_bands <- read_result("price_bands")
review_volume <- read_result("review_volume_distribution")
genre_summary <- read_result("genre_summary")
release_month <- read_result("release_month_summary")
model_comparison <- read_result("model_sample_comparison")
```

# Scope and semantics

This is SQL-first descriptive exploration. The market sample contains all 3,000
games, including zero- and low-review games. The model candidate sample is the
844 games with at least 20 Steam-purchase reviews. `total_reviews` is interpreted
only as a player-attention/market-engagement proxy, never sales. `positive_rate`
is observed Steam-review positivity and is used only when reviews exist. Prices
are collection-time storefront snapshots rather than launch or lifetime prices.

# Market structure

```{r}
knitr::kable(market, digits = 2)
```

Observed in this sample, `r market$free_games` games (`r market$free_share_pct`%)
are free and `r market$zero_review_games` (`r market$zero_review_share_pct`%)
have no reviews. Windows support is nearly universal; macOS and Linux support
are much less common.

# Collection-time price bands

```{r}
knitr::kable(price_bands, digits = 4)
```

Review volume is strongly skewed inside price bands, so medians and means are
shown together. These observed differences do not establish a price effect.

# Review-volume distribution

```{r}
knitr::kable(review_volume, digits = 4)
```

The first two bands contain `r sum(review_volume$games[1:2])` games, showing that
zero or single-digit review counts are common. The long upper tail motivates the
supplementary `LN(1 + total_reviews)` summary and robust statistics.

# Genre membership

```{r}
knitr::kable(genre_summary, digits = 4)
```

Genres are multi-label: membership counts and percentages are not mutually
exclusive, and genre counts can sum above 3,000.

# Release-month structure

```{r}
knitr::kable(release_month, digits = 4)
```

The table describes observed differences among the six sampled release months.
It does not identify seasonality or a causal month effect.

# Full market versus model candidate sample

```{r}
knitr::kable(model_comparison, digits = 4)
```

The >=20-review restriction materially changes sample composition, especially
free-game prevalence, observed price, genre mix, and attention. These selection
differences must be retained as a limitation in later modeling.

# Next questions

- Examine skew-aware visual summaries in Step 4B without discarding zero-review games.
- Assess uncertainty in raw positive rates, especially for low-review games.
- Consider Wilson intervals or empirical-Bayes shrinkage before rating comparisons.
- Explore price, genre, platform, and release-month associations without causal language.
- Diagnose selection into the >=20-review candidate sample before formal modeling.
